#Portfolio assignment 5
####*Experimental Methods 3*
**Helene Hauge Westerlund**  
11/12 2017  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***   

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia?

```{r}
setwd("C:/Users/Helene/Documents/RStudio working directory/Experimental Methods 3/Assignment-5")
Data = read.csv("C:/Users/Helene/Documents/RStudio working directory/Experimental Methods 3/Assignment-5/Data.csv", header=T, sep = ";")


library(pacman); library(metafor)

##MEAN
#Escalc
d_PitchMean = escalc('SMD', n1i= SampleSizeSchizo, n2i=SampleSizeContros, m1i= PitchMeanControls, m2i= PitchMeanSchizo, sd1i=PitchMeanControlsSD, sd2i=PitchMeanSchizoSD, data = Data)

#RMA
m1 = rma(yi, vi, data=d_PitchMean, slab=Article)

#Forest
forest(m1)
summary(m1)

#-----------------------------------
##SD
#Escalc
d_PitchSD = escalc('SMD', n1i= SampleSizeSchizo, n2i=SampleSizeContros, m1i= PitchSDControls, m2i= PitchSDSchizo, sd1i=PitchSDControlsSD, sd2i=PitchSDSchizoSD, data = Data)

#RMA
m2 = rma(yi, vi, data=d_PitchSD, slab=Article)

#Forest
forest(m2)
summary(m2)

```
Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 

***

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

shouldnt we also account for the analysis in assignment 3? we should extract the effect size from the analysis in assignment 3, and add this to the meta-analysis: simplest way to do this is standardise and scale data, and you can report the standardised beta as your yi, and vi is when you take variability of diagnosis and square that.
        vi = SD2 (variance of cohen's d)
        yi = standardised beta (Cohen's d)
        
```{r}
#Loading in own study
schizo_pitch_features = read.csv("schizo_pitch_features.csv")

#Getting mean and sd for controls
temp = subset(schizo_pitch_features,Diagnosis == "Control")
mean(temp$meanv)
mean(temp$sdv)

#Getting sd of mean and sd for controls
sd(temp$meanv)
sd(temp$sdv)

#Getting mean and sd for patients
temp1 = subset(schizo_pitch_features,Diagnosis == "Schizophrenia")
mean(temp1$meanv)
mean(temp1$sdv)

#Getting sd of mean and sd for patients
sd(temp1$meanv)
sd(temp1$sdv)

#Creating a new df with all this beautiful info
mydat = data.frame(Article = "my_data", Year = "2017", SampleSizeSchizo = 85, SampleSizeContros = 85, PitchMeanControls = 141.0266, PitchMeanControlsSD = 25.78532, PitchMeanSchizo = 149.0399, PitchMeanSchizoSD = 22.75408 , PitchSDControls = 49.09909, PitchSDControlsSD = 18.59616, PitchSDSchizo = 55.38506, PitchSDSchizoSD =32.83777)

Final_data = rbind(Data, mydat)


# #Running meta-analysis again

##MEAN
#Escalc
d_PitchMean = escalc('SMD', n1i= SampleSizeSchizo, n2i=SampleSizeContros, m1i= PitchMeanControls, m2i= PitchMeanSchizo, sd1i=PitchMeanControlsSD, sd2i=PitchMeanSchizoSD, data = Final_data)

#RMA
m3 = rma(yi, vi, data=d_PitchMean, slab=Article)

#Forest
forest(m3)
summary(m3)

#-----------------------------------
##SD
#Escalc
d_PitchSD = escalc('SMD', n1i= SampleSizeSchizo, n2i=SampleSizeContros, m1i= PitchSDControls, m2i= PitchSDSchizo, sd1i=PitchSDControlsSD, sd2i=PitchSDSchizoSD, data = Final_data)

#RMA
m4 = rma(yi, vi, data=d_PitchSD, slab=Article)

#Forest
forest(m4)
summary(m4)

```


3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.
[Funnel plot: When all the points are on one side, it can be sign of publication bias, because all the points that have been close to or under 0 (often middle line) have been ignored. Points outside the triangle are outliers. Ideally you would have a triangle with points evenly distributed on both sides (but nothing is rarely ideal).]

- Look at the output of rma() and check tau and I2
```{r}
#TAU^2: If tau^2>1, suggests a presence of substantial statistical heterogeneity.
#Rma output for mean
m3
#tau^2 = 0.0403

#Rma output for SD
m4
#tau^2 = 3.5084


#INFLUENTIAL STUDIES
inf_mean = influence(m3)
print(inf_mean)
plot(inf_mean)

inf_sd = influence(m4)
print(inf_sd)
plot(inf_sd)

#PUBLICATION BIAS
#Rank correlation test
ranktest(m3)
ranktest(m4)

#Funnel plots
funnel(m3, main = "Random-Effects Model", xlab = "Standardized Mean Difference")
funnel(m4, main = "Random-Effects Model", xlab = "Standardized Mean Difference")

#Assessing symmetry of funnel plots
regtest(m3,digits= 3)
regtest(m4,digits= 3)
```




[NOTES:


ESCALC('smd, n1i = sampleSeSchizo, ni1=, sc1i,

n2i = SampleSeSchizo, ni2=, sc2i')


lmer(ES~1 + (1|study), weights= 1/variance)


lm(yi~1, weights=1/vi, data)


lmer(yi~1 + (1|article) ((each article might be different from one another))


m1 = RMA(yi, vi, data, slab-article)

forest(m1) ((to get a forest plot))

]
